Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-03 envolve.tex
reconstruct logically
init on mac
start to deal with the user rank
give up simulation
add simple order flow
start the schedule and evolve modules.
first submit

% !TEX root = Eco-Model.tex
\section{Envolve} % (fold)
\label{sec:envolve}

% section envolve (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Manufacturing Ecosystem Envolving} % (fold)
\label{sec:envolve}
\subsection{Envolving Aim and Main Factors} % (fold)
\label{sub:envolving_aim}
The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operation mode for enterprises and filter out the underisable enterprises. In the process of envolving related 
main factors including:
\begin{inparaenum}[1)]
\item Rating Schema;
\item Recommand System and
\item Criterion of User Introduction and Elimination
\end{inparaenum}

\subsection{Rating Schema} % (fold)
\label{sub:rating_schema}
Rating user's rank is the base of Recommand System, from the time users were introduced in the system, their rank changing flow can be viewed like \autoref{fig:userrank}, 
\begin{figure}[!h]
\centering\small
\resizebox{0.6\textwidth}{!}{\input{figures/user_rank}}
\caption{Primary Flow of User Rank}
\label{fig:userrank}
\end{figure}
rating schema will be developed via the flow.

Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chessplayer, most modern rating systems are derived from Elo's model:

\begin{numcases}{}
E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \label{equ:elo1}\\
R_A := R_A + K(S_A - E_A) \label{equ:elo2} \\
E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \label{equ:elo3} \\
R_B := R_B + K(S_B - E_B) \label{equ:elo4} 
\end{numcases}
In \eqref{equ:elo1} - \eqref{equ:elo4}, $R_A$ and $R_B$ represent the rating of user $A$ and $B$, $E_A$ and $E_B$ represent the expected score of user $A$ and $B$ while $S_A$ and $S_B$ represent the actual score of them.

The assumption in the modle is that user's rank transfer from loser to winer, but there is no winner or loser in any transactions, so the modle should be reformed to suit the system.
% subsection rating_schema (end)

\subsection{Recommand System} % (fold)
\label{sub:recommand_system}
There are two scenarios in recommendation: \begin{inparaenum}[1)]
\item Service Searching and
\item Platform priority setting.
\end{inparaenum}
The first one is familar with the common use of recommend system, which use Collaboration Filtering method widely. Without no doubt, Collaboration Filtering Algorithm is the most popular algorithm in the recommand system, this algorithm use the history data of users' translations and their rated ratings, to archive customers and items simultaneously, then to make the recommendations. Let $r_{ui}$ be the rating made by user $u$ of item $i$ and $\hat{r}_{ui}$, the Latent Factor model\cite{koren2008factorization} using Collaboration Filtering algorithm goes like:

\begin{numcases}{}
\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
\label{equ:latent1}\\
\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
\end{numcases}
This model \eqref{equ:latent1} - \eqref{equ:elo4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet. \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector. This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.

The second one is also commonly used in nowadays business mode like Uber, administrator in platform analysed the resource load and other information of resource situation, made high priority of newly or low loaded resources by bonus to buysers.

% subsection recommand_system (end)

\subsection{User Introduction and Elimination} % (fold)
\label{sub:control}
Finally, administrators make the strategy for introduction and elimination of users, they can easily set a baseline and assess the user to make the decision.  
% subsection control (end)
% section envolve (end)

### 2015-10-03 schedule.tex
first submit

The scheduling effect can be estimated and observed through \textit{Service Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.

@@

Among these decisions, Order acceptance, Seller selection and Manufacturing arrangement can be descript as a classic order acceptance and scheduling problem, which has received increasing attention in recent years\cite{Og˘uz2010,Nobibon2011,Cesaret2012}. Task decomposition and (re-)outsourscing

@@

\subsection{Platform Assistance} % (fold)
\label{sub:platform_assistance}
a guide for scheduling 
% subsection platform_assistance (end)

\subsection{Service Dashboard} % (fold)
\label{sub:service_dashboard}
a monitor
% subsection service_dashboard (end)
% section model (end)

>>>>

The scheduling effect can be estimated and observed through \textit{Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.

@@

Among these decisions, Order acceptance, Seller selection and Manufacturing arrangement can be descript as a classic order acceptance and scheduling problem, which has received increasing attention in recent years\cite{Og˘uz2010,Nobibon2011,Cesaret2012}. Task decomposition and (re-)outsourscing can be descript as the decision making problem for users. Within the permission users get, they can tune the proportion of outsourscing.

@@

\subsection{Platform Assistance} % (fold)
\label{sub:platform_assistance}
Platform-auxiliary part of services scheduling is about the priority setting for tasks to be deal or for services to select, both are merely recommendation in the global view from administrator. Users can get bonus if they take the priority setting, but they won't get punishment if they don't.
As a result, two main issues have came: \begin{inparaenum}[1)]
\item How to make priority setting recommendation and
\item How to make decisions with the recommendation?
\end{inparaenum}
% subsection platform_assistance (end)

\subsection{Dashboard} % (fold)
\label{sub:service_dashboard}
Platform provides the Dashbord module for users to check the services usage and order process, comprehensive rank information, credit status and so on.
% subsection service_dashboard (end)
% section model (end)
